%Trends in Risk Factors for Lifestyle-Related Diseases in Geneva, Switzerland (1993-2004) by Socioeconomic Position Groups
%Populational Epidemiology Unit of the University Hospitals of Geneva
%Sierra Costanza, Yun (Albee) Ling, Bingjing Tang

```{r,echo=FALSE}
require(mmc2bsy)
```

Age Distributions Analysis (not reported)
=========================================
```{r,echo=FALSE}
data(Xm)
data(Xf)
AgeTest()
```

Table 1
=======
```{r,echo=FALSE}
table1(Xm)
table1(Xf)
```

Table B.1
=========
```{r,echo=FALSE}
tB1m=TableB1m()
tB1m
tB1f=TableB1f()
tB1f
```

Tables B.2 and B.3
==================
```{r,echo=FALSE}
tB2B3m=TablesB2B3m()
tB2B3f=TablesB2B3f()
```

Figure B.1
==========
```{r,echo=FALSE}
FigB1()
```

Figure B.2
==========
```{r,echo=FALSE}
FigB2()
```

Figure B.3
==========
```{r,echo=FALSE}
FigB3()
```

Figure B.4
==========
```{r,echo=FALSE}
FigB4()
```

Figure C.1
==========
```{r,echo=FALSE}
FigC1()
```

Model Selection Tables C.1-C.4
==============================
```{r,echo=FALSE}
Diagnostic()
```


```{r,eval=FALSE,include=FALSE}
knit('mmc2bsy.Rmd')
system('pandoc -s mmc2bsy.md -o mmc2bsy.tex')
system("pdflatex mmc2bsy.tex")
system("open mmc2bsy.pdf")
```
```